map

### 2022-03-01 Manuscript/Manuscript.tex
as

Palmer amaranth (\emph{Amaranthus palmeri} S. Watson) is currently
ranked as one of the most economically detrimental weed species to
cropping systems in the United States (Van Wychen, 2020). Unmanaged
Palmer amaranth plants compete for water, light, and nutrients, which
can drastically impact crop yields (Berger et al., 2015). For example,
Palmer amaranth has been documented to reduce up to 91\%, 68\%, and 54\%
corn (Massinga et al., 2001), soybean (Klingaman and Oliver, 1994), and
cotton (Morgan et al., 2001) yields, respectively. Moreover, Palmer
amaranth has shown a remarkable capacity to evolve resistance to
herbicides. To date, Palmer amaranth has evolved resistance to eight
herbicide sites of action (Heap, 2021), increasing the weed management
complexity (Lindsay et al., 2017) and posing an economical and
ecological risk to row-crop agriculture.

@@

The experiment was conducted in 2018 and 2019 under field conditions at
five locations: Arlington, WI (43°18'N, 89°29'W), Clay Center, NE
(40.57'N, 9814'W), Grant, NE (40.85'N, -101.70'W), Lincoln, NE (41.16'N,
96.42'W), and Macomb, IL (40.49'N, -90.69'W).

Fields were conventionally tilled prior to crop planting. Corn and
soybean were planted in 76-cm row spacing (Table 1). Monthly mean air
temperature and total precipitation were obtained using Daymet weather
data from June through September across the five locations in 2018 and
2019 (Correndo et al., 2021) (Figure 1).

@@

\caption{\label{tab:unnamed-chunk-2}Field study attributes }
\centering
\resizebox{\linewidth}{!}{
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lllllll}
\toprule
Attributes &  & Arlington, WI & Clay Center, NE & Grant, NE & Lincoln, NE & Macomb, IL\\
\midrule
Bareground &  &  &  &  &  & \\

 & Weed control & glyphosate & saflufenacil + imazethapyr + pyroxasulfone &  &  & \\

@@

 & Hybrid & NK0142 3120-EZ1 & DKC60-67 &  &  & \\

 & Seeding rate & 88956 & 86487 &  &  & \\

 & Weed control & glyphosate / S-metolachor & S-metolachlor + trazine + mesotrione, + bicyclopyrone &  &  & \\

 & Stage at 1 cohort & V2-3 &  &  &  & \\

 & Stage at 2 cohort & V6-7 &  &  &  & \\

 & Planting day & April 30, 2018 / May 5, 2019 & May 10, 2018/19 &  &  & \\

\multirow{-7}{*}{\raggedright\arraybackslash } & Fertilization & N (46-0-0) at 157 kg ha-1 &  &  &  & \\

@@

 & Type & Plano-silt-loam & Crete Silt Loam &  &  & \\

 & Ratio (sand-clay-silt) & 10-64-26 & 17-58-25 &  &  & \\

 & pH & 6.6 & 6.5 &  &  & \\

\multirow{-4}{*}{\raggedright\arraybackslash } & Organic matter (\%) & 3.5 & 3 &  &  & \\
\bottomrule
\multicolumn{7}{l}{\rule{0pt}{1em}\textsuperscript{a} glyphoste, 840 g ae ha \textsuperscript{b} S-metolachor, 1324 g ai ha; \textsuperscript{c} S-metolachlor + trazine + mesotrione, + bicyclopyrone, 2409 g ai ha; \textsuperscript{d} saflufenacil + imazethapyr + pyroxasulfone, 215 g ai ha}\\
\end{tabular}}
\end{table}

The field experimental units were three adjacent 9.1 m wide (12 rows at
76.2 cm row spacing) by 10.7 m long. The experimental design were
arranged in factorial design with three crops, two transplanting times
simulating two cohorts, repeated across five locations. Each field
experimental unit was planted with corn, soybean, or maintained as
bareground. The two transplant timings were June 1 (first cohort) and
July 1 (second cohort). Palmer amaranth seedlings (potting mix + two
seedlings) were transplanted (6 cm deep and 8 cm wide). Forty-eight
plants were equidistantly placed (0.76 m apart) between rows within each
crop. After a week, one plant was eliminated and one was kept, resulting
in 24 plants per experimental unit and transplanting time (Figure 2).
When needed, Palmer amaranth plants were supplied with water during the
first week after transplanting to assure seedling survival.

@@

Palmer amaranth plants accumulated more biomass when growing in
bareground compared to plants growing in soybean and corn (Figure 3A).
Palmer amaranth plants in the first cohort produced 75.5, 28.3, and 16.3
g plant\textsuperscript{-1} in bareground, soybean and corn,
respectively. Plants from the second cohort produced 62.6 g
plant\textsuperscript{-1} in bareground, followed by 6.3 g
plant\textsuperscript{-1} in soybean, and 1.4 g
plant\textsuperscript{-1} in corn.

Palmer amaranth height was less affected by cohort timing than was
weight, with the exception of plants growing in corn (Figure 3B). Plants
from the first cohort were on average 69.2 cm tall in bareground, which
was not different from the 70.7 cm tall plants from the second cohort
timing (P = 0.74). In addition, no difference in Palmer amaranth height
(69.3 cm) was detected from first cohort plants in soybean to first and
second cohort plants in bareground (P \textgreater{} 0.75). Palmer
amaranth plants from the second cohort were nearly 10 cm shorter
compared to the first cohort in soybeans (P = 0.04). The tallest (85.2
cm, first cohort) and shortest (38.2 cm, second cohort) plants were
observed in corn.

@@

The initiation and duration of Palmer amaranth flowering were strongly
influenced by cohort and surrounding vegetation (Figure 4A, 4B). In the
first cohort, floral initiation (10\% flowering) occurred near the end
of June for all three treatments, at doy 180, 180.9, and 181.7 for
soybean, bareground, and corn, respectively. In the second cohort,
floral initiation occurred earlier on plants growing in the bareground
than plants growing in soybean or corn (doy 203.8 versus doy 210.9 or
216.8, respectively). Palmer amaranth growing in the bareground had the
shortest flowering initiation (measured as the difference between 10\%
and 90\% cumulative flowering) in both the first (34 days) and second
(28 days) cohorts. Palmer amaranth growing in soybean had a shorter
duration of flowering than corn in the first cohort (40 days vs 71
days), but a longer duration in the second cohort (50 vs 44 days).

Palmer amaranth cumulative flowering in the second cohort occurred from
mid July to mid September (Figure 4B). Palmer amaranth growing in the
bareground resulted in earlier flowering time compared to soybean and
corn. Palmer amaranth growing in bareground reached 10\%, 50\%, and 90\%
flowering time at day 203.8, 214.4, and 232.2, respectively. Palmer
amaranth growing in soybean reached 10\% flowering at doy 210.9, which
was 6 days prior to corn (\emph{P}-value = 0.00). Similar trend was
observed at 50\% flowering, whereas Palmer amaranth reached 50\%
flowering in corn (doy 233.0) 4 days after soybeans (doy 228.9; \emph{P}
= 0.00). The 90\% Palmer amaranth cumulative flowering occurred at same
day in corn (260.9) and soybean (260.5; \emph{P} = 0.66).

@@

The model goodness of fit was 0.23, 0.32, 0.40 using pseudo R-squared
test from McFadden, Cox and Snell, and Cragg and Uhler, respectively.
The likelihood ratio test showed a p-value of \textless{} 0.00. The
average marginal effects showed that Palmer amaranth growing in corn
resulted in 14.8\% fewer females plants (Table 2). Moreover, increasing
a cumulative flowering unit doy increases the probability of having a
female plant by 0.4\% (Table 2 and Figure5A). A similar trend was
observed for weight (Figure 5B) and height (Figure 5C), where the
probability of being female increased 0.1\% and 0.2\% for each unit
increase of weight and height, respectively (Table 2).

\textbackslash begin\{table\}{[}!h{]}

\textbackslash caption\{\label{tab:unnamed-chunk-3}Average marginal
effects of Palmer amaranth gender logistic model. Factor pararemter
values (crop\_corn and 'crop\_bareground) are calculated relative to
soybean.\} \centering \fontsize{10}{12}\selectfont

\begin{tabular}[t]{lrrrrrr}
\toprule
Term & AME & SE & Lower & Upper & Z-score & P-value\\
\midrule
crop\_bareground & -0.048 & 0.054 & -0.154 & 0.059 & -0.876 & 0.381\\

@@

Our study demonstrate that Palmer amaranth is well adapted to growing
conditions throughout the Midwestern United States, and is simply
limited in its range by seed dispersal (Davis et al.~2015). We also
confirmed Palmer amaranth's extraordinary plasticity to adapt to
different agroecosystems. For example, Palmer amaranth mimicked crop
architecture in competing for light (Figure 6), where plants growing in
corn allocated resources to height, while plants growing in bareground
allocated resources to numerous branches. Plants growing in the absence
of a crop produced the greatest biomass, responding to a greater
abundance of light, nutrient and water resources (Figure 3A, 3B). These
results support the argument that Palmer amaranth can quickly evolve
life-history traits to adapt to different cultural practices, similar to
observations in a Palmer amaranth response to nitrogen study (Bravo et
al., 2018). Our results highlight Palmer amaranth as a threat to field
crops and breeding more competitive crop varieties is likely to select
more competitive weed biotypes (Bravo et al., 2017).

@@

\leavevmode\hypertarget{ref-heap2021}{}%
Heap, I. (2021). Internation {Herbicide}-{Resistant Weed Database}.
Available at: \url{http://www.weedscience.org/Home.aspx} {[}Accessed
July 26, 2021{]}.

@@

\leavevmode\hypertarget{ref-rcoreteam2021}{}%
Team, R. C. (2021). \emph{R: {The R Project} for {Statistical
Computing}}. {Vienna, Austria}: {R Foundation for Statistical Computing}
Available at: \url{https://www.r-project.org/} {[}Accessed August 24,
2021{]}.

@@

{\centering \includegraphics[width=160mm,height=100mm]{../data analysis/weather/Figure 1}

@@

\caption{Mean average temperature (C) and total montly precipitation (mm) at Arlington, WI, Clay Center, NE, Grant, NE, Lincoln, NE and Macomb, IL.}\label{fig:Figure-1}
\end{figure}

@@

{\centering \includegraphics[width=150mm,height=70mm]{../data analysis/figures/Figure 2}

@@

\caption{Palmer amaranth adaptation study layout of a plant cohort timing in bareground, corn, and soybean. Twenty-four Palmer amaranth plants were place 76.2 cm apart in each field experimental unit.}\label{fig:Figure-2}
\end{figure}

@@

{\centering \includegraphics[width=150mm,height=90mm]{../data analysis/figures/Figure 3}

@@

\caption{Palmer amaranth biomass (A) and height (B) growing in corn, bareground, and soybean nested across Arlington, WI, Clay Center, NE, Grant, NE, Lincoln, NE and Macomb, IL.}\label{fig:Figure-3}
\end{figure}

@@

{\centering \includegraphics[width=150mm,height=150mm]{../data analysis/figures/Figure 4}

@@

\caption{Cumulative flowering of Palmer amaranth at first and second transplant timing (A) and day of year of 10, 50, and 90 cumulative flowering at first and second cohort transplanting time (B) nested across Arlington, WI, Clay Center, NE, Grant, NE, Lincoln, NE and Macomb, IL.}\label{fig:Figure-4}
\end{figure}

@@

{\centering \includegraphics[width=170mm,height=70mm]{../data analysis/figures/Figure 5}

@@

\caption{The probability (P) of being female Palmer amaranth by day of year (A), weight (B), and height (C). Black line represents the model estimation and shaded green the confidence intervals.}\label{fig:Figure-5}
\end{figure}

@@

{\centering \includegraphics[width=150mm,height=90mm]{../data analysis/figures/Figure 6}

@@

\caption{MCO (180 cm) holds harvested Palmer amaranth plants at 40 days after first cohort transplanting (A) and 33 days after second cohort transplanting (B) time. From left to right in each image, Palmer amaranth growing in bareground, soybean and corn in Arlington, Wisconsin.}\label{fig:Figure-6}
\end{figure}

>>>>

Palmer amaranth (\emph{Amaranthus palmeri} S. Watson) is currently
ranked as one of the most economically detrimental weed species to
cropping systems in the United States (Van Wychen, 2020). Unmanaged
Palmer amaranth plants compete for water, light, and nutrients, which
can drastically impact crop yields (Berger et al., 2015). For example,
Palmer amaranth has been documented to reduce up to 91\%, 68\%, and 54\%
corn (Massinga et al., 2001), soybean (Klingaman and Oliver, 1994), and
cotton (Morgan et al., 2001) yields, respectively. Moreover, Palmer
amaranth has shown a remarkable capacity to evolve resistance to
herbicides. To date, Palmer amaranth has evolved resistance to eight
herbicide sites of action (Heap, 2022), increasing the weed management
complexity (Lindsay et al., 2017) and posing an economical and
ecological risk to row-crop agriculture.

@@

The experiment was conducted in 2018 and 2019 under field conditions at
five locations: Arlington, WI, Clay Center, NE,, Grant, NE, Lincoln, NE,
and Macomb, IL.

Fields were conventionally tilled prior to crop planting. Corn and
soybean were planted in 76-cm row spacing (Table 1). Monthly mean air
temperature and total precipitation were obtained using Daymet weather
data from June through September across the five locations in 2018 and
2019 (Correndo et al., 2021) (Figure 2).

@@

\caption{\label{tab:unnamed-chunk-2}Field study attributes from Arlington, WI, Clay Center, NE, Grant, NE, Lincoln, NE and Macomb, IL.}
\centering
\resizebox{\linewidth}{!}{
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lllllll}
\toprule
Attributes &  & Arlington, WI & Clay Center, NE & Grant, NE & Lincoln, NE & Macomb, IL\\
\midrule
Bareground &  &  &  &  &  & \\

 & Weed control\textsuperscript{a} & \emph{S}-metolachor\textsuperscript{b} fb glyphosate\textsuperscript{c}  & saflufenacil + imazethapyr + pyroxasulfone\textsuperscript{d} & glyphosate\textsuperscript{c} & glyphosate + \emph{S}-metolachor\textsuperscript{f} fb glyphosate\textsuperscript{g} & glyphosate + \emph{S}-metolachor\textsuperscript{f} \\

@@

 & Hybrid & NK0142 3120-EZ1 & DKC60-67 & G03C84-5122-EZ1 & P1197AM & DKC64-34RIB (2018) / G10T63-3000GT (2019) \\

 & Seeding rate & 88956 & 86487 & 79000 & 86485 & 88,000 (2018) / 79,000 (2019)\\

 & Weed control & \emph{S}-metolachor fb glyphosate & \emph{S}-metolachlor + trazine + mesotrione + bicyclopyrone\textsuperscript{e} & glyphosate & glyphosate + \emph{S}-metolachor\textsuperscript{f} fb glyphosate\textsuperscript{g} & glyphosate + \emph{S}-metolachor \\

 & Stage at 1\textsuperscript{st} cohort & V2-3 & V2-3 & V2-3 & V2-3 & V4-5\\

 & Stage at 2\textsuperscript{nd} cohort & V6-7 & V6-7 & V6-7 & V6-7 & V10-11\\

 & Planting day & April 30, 2018 / May 5, 2019 & May 10, 2018/19 & May 5, 2018 / May 14, 2019 & April 27, 2018 / May 3, 2019 & May 8, 2018 / April 26, 2019 \\

\multirow{-7}{*}{\raggedright\arraybackslash } & Fertilization & N (46-0-0) at 157 kg ha\textsuperscript{-1} &  &  & N (46-0-0) at 336 kg ha\textsuperscript{-1} & UAN-32, 202 kg N ha\textsuperscript{-1}\\

@@

 & Type & Plano-silt-loam & Crete Silt Loam & 2018: Mace silt loam / 2019: Kuma silt loam & Crete silty clay loam & \\

 & pH & 6.6 & 6.5 & 2018: 6.1 / 2019: 5.1 & 5.2 & \\

\multirow{-4}{*}{\raggedright\arraybackslash } & Organic matter (\%) & 3.5 & 3 & 2018: 2 / 2019: 1.7 & 3.4 & \\
\bottomrule
\multicolumn{7}{l}{\rule{0pt}{1em}\textsuperscript{a}Hoe weeding; \textsuperscript{b}\emph{S}--metolachor, 1324 g ai ha\textsuperscript{-1}; \textsuperscript{c}glyphoste, 1262 g ae ha\textsuperscript{-1}; \textsuperscript{d}saflufenacil + imazethapyr + pyroxasulfone, 215 g ai ha\textsuperscript{-1}; \textsuperscript{e}\emph{S}-metolachlor + trazine + mesotrione, + bicyclopyrone, 2409 g ai ha\textsuperscript{-1}; \textsuperscript{f}\emph{S}--metolachor, 1070 g ai ha\textsuperscript{-1}; \textsuperscript{g}glyphoste, 870 g ae ha\textsuperscript{-1}} \\
\end{tabular}}
\end{table}

The field experimental units were three adjacent 9.1 m wide (12 rows at
76.2 cm row spacing) by 10.7 m long. The experimental design were
arranged in factorial design with three crops, two transplanting times
simulating two cohorts, repeated across five locations. Each field
experimental unit was planted with corn, soybean, or maintained as
bareground. The two transplant timings were June 1 (first cohort) and
July 1 (second cohort). Palmer amaranth seedlings (potting mix + two
seedlings) were transplanted (6 cm deep and 8 cm wide). Forty-eight
plants were equidistantly placed (0.76 m apart) between rows within each
crop. After a week, one plant was eliminated and one was kept, resulting
in 24 plants per experimental unit and transplanting time (Figure 3).
When needed, Palmer amaranth plants were supplied with water during the
first week after transplanting to assure seedling survival.

@@

Palmer amaranth plants accumulated more biomass when growing in
bareground compared to plants growing in soybean and corn (Figure 4A).
Palmer amaranth plants in the first cohort produced 75.5, 28.3, and 16.3
g plant\textsuperscript{-1} in bareground, soybean and corn,
respectively. Plants from the second cohort produced 62.6 g
plant\textsuperscript{-1} in bareground, followed by 6.3 g
plant\textsuperscript{-1} in soybean, and 1.4 g
plant\textsuperscript{-1} in corn.

Palmer amaranth height was less affected by cohort timing than was
weight, with the exception of plants growing in corn (Figure 4B). Plants
from the first cohort were on average 69.2 cm tall in bareground, which
was not different from the 70.7 cm tall plants from the second cohort
timing (P = 0.74). In addition, no difference in Palmer amaranth height
(69.3 cm) was detected from first cohort plants in soybean to first and
second cohort plants in bareground (P \textgreater{} 0.75). Palmer
amaranth plants from the second cohort were nearly 10 cm shorter
compared to the first cohort in soybeans (P = 0.04). The tallest (85.2
cm, first cohort) and shortest (38.2 cm, second cohort) plants were
observed in corn.

@@

The initiation and duration of Palmer amaranth flowering were strongly
influenced by cohort and surrounding vegetation (Figure 5A, 4B). In the
first cohort, floral initiation (10\% flowering) occurred near the end
of June for all three treatments, at doy 180, 180.9, and 181.7 for
soybean, bareground, and corn, respectively. In the second cohort,
floral initiation occurred earlier on plants growing in the bareground
than plants growing in soybean or corn (doy 203.8 versus doy 210.9 or
216.8, respectively). Palmer amaranth growing in the bareground had the
shortest flowering initiation (measured as the difference between 10\%
and 90\% cumulative flowering) in both the first (34 days) and second
(28 days) cohorts. Palmer amaranth growing in soybean had a shorter
duration of flowering than corn in the first cohort (40 days vs 71
days), but a longer duration in the second cohort (50 vs 44 days).

Palmer amaranth cumulative flowering in the second cohort occurred from
mid July to mid September (Figure 5B). Palmer amaranth growing in the
bareground resulted in earlier flowering time compared to soybean and
corn. Palmer amaranth growing in bareground reached 10\%, 50\%, and 90\%
flowering time at day 203.8, 214.4, and 232.2, respectively. Palmer
amaranth growing in soybean reached 10\% flowering at doy 210.9, which
was 6 days prior to corn (\emph{P}-value = 0.00). Similar trend was
observed at 50\% flowering, whereas Palmer amaranth reached 50\%
flowering in corn (doy 233.0) 4 days after soybeans (doy 228.9; \emph{P}
= 0.00). The 90\% Palmer amaranth cumulative flowering occurred at same
day in corn (260.9) and soybean (260.5; \emph{P} = 0.66).

@@

The model goodness of fit was 0.23, 0.32, 0.40 using pseudo R-squared
test from McFadden, Cox and Snell, and Cragg and Uhler, respectively.
The likelihood ratio test showed a p-value of \textless{} 0.00. The
average marginal effects showed that Palmer amaranth growing in corn
resulted in 14.8\% fewer females plants (Table 2). Moreover, increasing
a cumulative flowering unit doy increases the probability of having a
female plant by 0.4\% (Table 2 and Figure5A). A similar trend was
observed for weight (Figure 6B) and height (Figure 6C), where the
probability of being female increased 0.1\% and 0.2\% for each unit
increase of weight and height, respectively (Table 2).

\caption{\label{tab:unnamed-chunk-3}Average marginal means of Palmer amaranth sex dimorphism logistic model. Factor pararemter values (crop\_bareground and crop\_corn) is shown compared to soybean.}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lrrrrrr}
\toprule
Term & AME\textsuperscript{a} & SE\textsuperscript{b} & Lower & Upper & Z-score & P-value\\
\midrule
crop\_bareground & -0.048 & 0.054 & -0.154 & 0.059 & -0.876 & 0.381\\

@@

Our study demonstrate that Palmer amaranth is well adapted to growing
conditions throughout the Midwestern United States, and is simply
limited in its range by seed dispersal (Davis et al.~2015). We also
confirmed Palmer amaranth's extraordinary plasticity to adapt to
different agroecosystems. For example, Palmer amaranth mimicked crop
architecture in competing for light (Figure 7), where plants growing in
corn allocated resources to height, while plants growing in bareground
allocated resources to numerous branches. Plants growing in the absence
of a crop produced the greatest biomass, responding to a greater
abundance of light, nutrient and water resources (Figure 4A, 3B). These
results support the argument that Palmer amaranth can quickly evolve
life-history traits to adapt to different cultural practices, similar to
observations in a Palmer amaranth response to nitrogen study (Bravo et
al., 2018). Our results highlight Palmer amaranth as a threat to field
crops and breeding more competitive crop varieties is likely to select
more competitive weed biotypes (Bravo et al., 2017).

@@

\leavevmode\hypertarget{ref-heap2022}{}%
Heap, I. (2022). Internation {Herbicide}-{Resistant Weed Database}.
Available at: \url{http://www.weedscience.org/Home.aspx} {[}Accessed
January 26, 2022{]}.

@@

\leavevmode\hypertarget{ref-rcoreteam2021}{}%
R Core Team (2021). \emph{R: {The R Project} for {Statistical
Computing}}. {Vienna, Austria}: {R Foundation for Statistical Computing}
Available at: \url{https://www.r-project.org/} {[}Accessed August 24,
2021{]}.

@@

{\centering \includegraphics[width=160mm,height=90mm]{../data analysis/figures/Figure 1}

@@

\caption{Field research locations in the United States North Central region.}\label{fig:Figure-1}
\end{figure}

@@

{\centering \includegraphics[width=160mm,height=100mm]{../data analysis/weather/Figure 2}

@@

\caption{Mean average temperature (C) and total montly precipitation (mm) at Arlington, WI, Clay Center, NE, Grant, NE, Lincoln, NE and Macomb, IL.}\label{fig:Figure-2}
\end{figure}

@@

{\centering \includegraphics[width=150mm,height=70mm]{../data analysis/figures/Figure 3}

@@

\caption{Palmer amaranth adaptation study layout of a plant cohort timing in bareground, corn, and soybean. Twenty-four Palmer amaranth plants were place 76.2 cm apart in each field experimental unit.}\label{fig:Figure-3}
\end{figure}

@@

{\centering \includegraphics[width=150mm,height=90mm]{../data analysis/figures/Figure 4}

@@

\caption{Palmer amaranth biomass (A) and height (B) growing in corn, bareground, and soybean nested across Arlington, WI, Clay Center, NE, Grant, NE, Lincoln, NE and Macomb, IL.}\label{fig:Figure-4}
\end{figure}

@@

{\centering \includegraphics[width=150mm,height=150mm]{../data analysis/figures/Figure 5}

@@

\caption{Cumulative flowering of Palmer amaranth at first and second transplant timing (A) and day of year of 10, 50, and 90 cumulative flowering at first and second cohort transplanting time (B) nested across Arlington, WI, Clay Center, NE, Grant, NE, Lincoln, NE and Macomb, IL.}\label{fig:Figure-5}
\end{figure}

@@

{\centering \includegraphics[width=170mm,height=70mm]{../data analysis/figures/Figure 6}

@@

\caption{The probability (P) of being female Palmer amaranth by day of year (A), weight (B), and height (C). Black line represents the model estimation and shaded green the confidence intervals.}\label{fig:Figure-6}
\end{figure}

{\centering \includegraphics[width=150mm,height=90mm]{../data analysis/figures/Figure 7}

\caption{MCO (first manuscript author, 180 cm) holds harvested Palmer amaranth plants at 40 days after first cohort transplanting (A) and 33 days after second cohort transplanting (B) time. From left to right in each image, Palmer amaranth growing in bareground, soybean and corn in Arlington, Wisconsin.}\label{fig:Figure-7}
\end{figure}

### 2022-03-01 data analysis/Untitled.Rmd
as

```{r}
#  US National Atlas Equal Area projection (CRS 2163)
usa <- subset(world, admin == "United States of America")
(mainland <- ggplot(data = usa) +
    geom_sf(fill = "cornsilk") +
    geom_sf(data = sites, size = 3, shape = c(15, 16, 17, 18, 19)) +
    coord_sf(crs = st_crs(2163), xlim = c(-2500000, 2500000), ylim = c(-2300000, 
         730000)))
```

@@

```{r}
library(grid)
library(ggrepel)
mainland +
 annotation_custom(
      grob = ggplotGrob(alaska),
      xmin = -2750000,
      xmax = -2750000 + (1600000 - (-2400000))/2.5,
      ymin = -2450000,
      ymax = -2450000 + (2500000 - 200000)/2.5
  ) +
  annotation_custom(
      grob = ggplotGrob(hawaii),
      xmin = -1250000,
      xmax = -1250000 + (-154 - (-161))*120000,
      ymin = -2450000,
      ymax = -2450000 + (23 - 18)*120000
  ) +
  annotation_custom(textGrob(label="Grant, NE", x = 0.40, y = 0.605)) +
  annotation_custom(textGrob(label="Arlington, WI", x = 0.65, y = 0.75)) +
  annotation_custom(textGrob(label="Macomb, IL", x = 0.73, y = 0.60)) +
  annotation_custom(textGrob(label="Lincoln, NE", x = 0.60, y = 0.65)) +
  annotation_custom(textGrob(label="Clay Center, NE", x = 0.58, y = 0.55)) +
  annotation_scale(location = "br", width_hint = 0.25) +
  annotation_north_arrow(location = "tl", which_north = "true", 
        pad_x = unit(0.1, "in"), pad_y = unit(0.1, "in"),
        style = north_arrow_nautical) 
 # geom_sf_text(data = sites, aes(label = location))

@@

```{r}
library(cowplot)
# Using cowplot
(ratioAlaska <- (2500000 - 200000) / (1600000 - (-2400000)))
(ratioHawaii  <- (23 - 18) / (-154 - (-161)))
ggdraw(mainland) +
    draw_plot(alaska, width = 0.26, height = 0.26 * 10/6 * ratioAlaska, 
        x = 0.05, y = 0.05) +
    draw_plot(hawaii, width = 0.15, height = 0.15 * 10/6 * ratioHawaii, 
        x = 0.3, y = 0.05) +
  annotate("text", label = "Arlington, WI", x = 90, y = 40)
```

>>>>

```{r}
#  US National Atlas Equal Area projection (CRS 2163)
usa <- subset(world, admin == "United States of America")
(mainland <- ggplot(data = usa) +
    geom_sf(fill = "cornsilk") +
    geom_sf(data = sites, size = 2, shape = c(15, 16, 17, 18, 19)) +
    coord_sf(crs = st_crs(2163), xlim = c(-2500000, 2500000), ylim = c(-2300000, 
         730000)))
```

@@

```{r}
library(grid)
library(ggrepel)
library(ggspatial)
library(ggsflabel)
library(cowplot)
mainland +
 annotation_custom(
      grob = ggplotGrob(alaska),
      xmin = -2750000,
      xmax = -2750000 + (1600000 - (-2400000))/2.5,
      ymin = -2450000,
      ymax = -2450000 + (2500000 - 200000)/2.5
  ) +
  annotation_custom(
      grob = ggplotGrob(hawaii),
      xmin = -1250000,
      xmax = -1250000 + (-154 - (-161))*120000,
      ymin = -2450000,
      ymax = -2450000 + (23 - 18)*120000
  ) +
#  annotation_custom(textGrob(label="Grant, NE", x = 0.40, y = 0.605)) +
#  annotation_custom(textGrob(label="Arlington, WI", x = 0.65, y = 0.75)) +
#  annotation_custom(textGrob(label="Macomb, IL", x = 0.73, y = 0.60)) +
#  annotation_custom(textGrob(label="Lincoln, NE", x = 0.60, y = 0.65)) +
#  annotation_custom(textGrob(label="Clay Center, NE", x = 0.58, y = 0.55)) +
  annotation_scale(location = "br", width_hint = 0.25) +
  annotation_north_arrow(location = "tl", which_north = "true", 
        pad_x = unit(0.1, "in"), pad_y = unit(0.1, "in"),
        style = north_arrow_nautical) +
  geom_sf_text_repel(data = sites, aes(label = location), size = 2.5,
                     min.segment.length = 1, point.padding = 0.5, 
                     box.padding = 0.25,
                     max.overlaps = 10,
                     seed = 564,
                     max.iter = 10000,
                     segment.color = 'grey50') +
  labs(x= NULL, y = NULL)

@@
